Supplemental Material for: The evolution of gene expression in the term placenta of viviparous mammals

### 2016-03-11 manuscript/supplemental_material.Rnw
add the GSE numbers to the supplement and the manuscript

    \textit{Ateles fusciceps}     & Kurt Benirschke & & \\
    \textit{Bos taurus}           & Bob Kreft & & \\
    \textit{Canis familiaris}     & Dalen Agnew & & (Bounty Hubler) \\
    \textit{Dasypus novemcinctus} & Richard Truman, Vincent J. Lynch& & \\

@@

    \textit{Loxodonta africana}   & Kurt Benirschke & & \\

@@

    \textit{Monodelphis domestica} & Karen Smith, Gunter Wagner & & \\

@@

    \textit{Pan paniscus}         & William Mintz Fields & & (Teco)\\

>>>>

    \textit{Ateles fusciceps}     & Kurt Benirschke & GSE79121 & \\
    \textit{Bos taurus}           & Bob Kreft & GSE79121 & \\
    \textit{Canis familiaris}     & Dalen Agnew & GSE79121 & (Bounty Hubler) \\
    \textit{Dasypus novemcinctus} & Richard Truman, Vincent J. Lynch& GSE79121 & \\

@@

    \textit{Loxodonta africana}   & Kurt Benirschke & GSE79121 & \\

@@

    \textit{Monodelphis domestica} & Karen Smith, Gunter Wagner & GSE79121 & \\

@@

    \textit{Pan paniscus}         & William Mintz Fields & GSE79121 & (Teco) \\
